---
title: "Data Upload"
author: "Author"
date: "2025-03-28"
output: html_document
---


### Introduction
This Rmarkdown reads in and cleans data collected on Kestrel D2 drop humidity loggers collected in Summer 2020 on 10 separate days. Each day had 7 loggers deployed, with a varying number of treatments and replicates based on the evolving nature of the experimental question. 

## Install Libraries
```{r}
library(dplyr)
library(lubridate)
library(tidyverse)
library(readr)
```

## Functions to Read Data

```{r}
## Editing Kestrel Function data script to wrangle uploaded data
edit_Kestrel <- function(dfK_raw, filename){
  
  # Pull serial number which is saved in row 2 column 2
  serial_number <- as.character(dfK_raw[2, 2]) 
  
  # Skip the first 4 rows
  dfK <- dfK_raw[-c(1:4), ]  
  
  # Save treatment which was manually included in the file name as "-treatment.csv"
  treatment <- str_extract(basename(filename), "(?<=-)[^\\.]+") 
  
  # Change column names
  colnames(dfK) <- c("DateTime","Temp","RH","Heat_Stress","Dew_Point")
  
  # Subset relevant columns
  dfK <- dplyr::select(dfK, DateTime, Temp, RH) 
  
  # Correct data type
  dfK$Temp= as.double(dfK$Temp)
  dfK$RH = as.double(dfK$RH)
  dfK$DateTime <- mdy_hm(dfK$DateTime)

  # Create new columns
  dfK <- mutate(dfK, Time = strftime(dfK$DateTime, format = "%H:%M:%S %p", tz = "UTC"), .before = Temp) #separates time as character 
  dfK$Time <- substr(dfK$Time, 1, 5) #removes seconds from Time
  
  dfK <- mutate(dfK, Date = as.Date(dfK$DateTime), .before = Time) #adds date column

  dfK <- mutate(dfK, SerialNumber = serial_number) #adds serial number 
  dfK <- mutate(dfK, Treatment = treatment) #adds treatment

  return(dfK)
}
```

### Read In Data
```{r}
# Define the folder path
folder_path <- "../01_RawData"

file_list <- list.files(path = folder_path, pattern = "*.csv", full.names = TRUE)

process_file <- function(file) {
  df <- read_csv(file, show_col_types = FALSE)  # Read raw file
  df <- edit_Kestrel(df, file)  # Pass both dataframe and filename
  return(df)
}

combined_df <- bind_rows(lapply(file_list, process_file))

glimpse(combined_df)
```
### Now for every day, it looks like I cut out some amount of time, I need to investigate if they are the same and document why and then I'm thinking I save in a separate csv and then call on that to the cut the times in the combined.df


